Human capital drives natural selection in contemporary humans

### 2021-04-15 why-natural-selection.Rmd
small tweaks

* Add CIs - done.
* Clarify collider bias/endogeneity - done.
* Formalize theory - done.
  - Comment on results where effects are actually reversed. Could this
  happen if \sigma were higher in period 2? Or if it increased with income?
  Could maybe do a computational example.
  - One possibility is CARA utility. Solving it computationally
* Clarify causality?
  - Helps to deal with the "collider bias" argument of reviewer
  - Might also be a better test of mediation via human capital
  - One other possibility. If we use only people with first profession
    teacher, that (as it happens) shuts down the EA3-income correlation.
    It also shuts down the EA3-fertility relationship, suggesting that
    income is indeed the mediator.
* Control for PGS for fertility
* Clarify "what we learn about genetic links to fertility by using economic theory to interpret relationships between polygenic scores and fertility."
  - Point is that we can explain how natural selection is occurring.
* "Discuss empirical predictions for AFLB grounded in dynamic theory"
  - hmm, tricky, maybe we can include it in discussion of economic results at
  end of formal section.
* Why don't women see stronger effects? But note, they do: not significant
  after correction for multiple testing, but a 25% difference.

@@

We also check for purifying and diversifying selection by 
estimating \@ref(eq:regression) with a quadratic term. See Appendix Figure \@ref(fig:plot-purifying). In particular, we find diversifying selection for
educational attainment polygenic scores: at higher values of these scores, 
the effect on fertility is closer to zero.

@@

res_wt_combined %>% 
  mutate(
    Weights  = fct_relevel(Weights, "Geographical", "Age/Qualification",
                "Age/Qual/AFLB", "None"),
    term     = pretty_names(term),
    term     = fct_reorder(term, estimate, order_abs(1))
  ) %>% 
  rename(p = p.value) %>% 
  ggplot(aes(
    x = estimate, 
    y = term, 
    shape = Weights, 
    fill = Weights, 
    colour = p < 0.05/{{n_regs}}
  )) +
  geom_point(size = 1.5, stroke = 0.5) +
  my_vline +
  pval_scale() +
  scale_fill_manual(values = c(
    "None"              = "grey15", 
    "Geographical"      = "dodgerblue4",
    "Age/Qualification" = "steelblue2",
    "Age/Qual/AFLB"      = "darkseagreen4"
  )) +
  scale_shape_manual(values = c(
    "None" = "square filled", 
    "Geographical" = "circle filled",
    "Age/Qualification" = "circle filled", 
    "Age/Qual/AFLB" = "circle filled"
  )) + 
  labs(x = "Effect size", y = "") +
  my_theme()

>>>>

* Add CIs - done.
* Clarify collider bias/endogeneity - done.
* Formalize theory - done.
  - Comment on results where effects are actually reversed. This works
    nicely if you throw in a money cost. Done computational example.
* Clarify causality?
  - Helps to deal with the "collider bias" argument of reviewer
  - Might also be a better test of mediation via human capital
  - One other possibility. If we use only people with first profession
    teacher, that (as it happens) shuts down the EA3-income correlation.
    It also shuts down the EA3-fertility relationship, suggesting that
    income is indeed the mediator.
* Control for PGS for fertility
* Clarify "what we learn about genetic links to fertility by using economic theory to interpret relationships between polygenic scores and fertility."
  - Point is that we can explain how natural selection is occurring.
* "Discuss empirical predictions for AFLB grounded in dynamic theory"
  - hmm, tricky, maybe we can include it in discussion of economic results at
  end of formal section.
* Why don't women see stronger effects? But note, they do: not significant
  after correction for multiple testing, but a 25% difference. 
  - I think we leave this for reviewers.

@@

We also check for purifying and diversifying selection by estimating
\@ref(eq:regression) with a quadratic term. In particular, we find diversifying
selection for educational attainment polygenic scores: at lower values of these
scores, the negative effect on fertility is larger (Appendix Figure
\@ref(fig:plot-purifying)).

@@

res_wt_combined %>% 
      mutate(
        Weights  = fct_relevel(Weights, "Geographical", "Age/Qualification",
                    "Age/Qual/AFLB", "None"),
        term     = pretty_names(term),
        term     = fct_reorder(term, estimate, order_abs(1))
      ) %>% 
      rename(p = p.value) %>% 
      # can't use standard_ggplot because we have non-standard geom_point()
      ggplot(aes(
        x      = estimate, 
        y      = term, 
        yend   = term,
        shape  = Weights, 
        fill   = Weights, 
        colour = p < 0.05/{{n_regs}}
      )) +
      my_vline +
      geom_point(size = 1.5, stroke = 0.5) +
      confint_geom_segment() +
      pval_scale() +
      scale_fill_manual(values = c(
        "None"              = "grey15", 
        "Geographical"      = "dodgerblue4",
        "Age/Qualification" = "steelblue2",
        "Age/Qual/AFLB"      = "darkseagreen4"
      )) +
      scale_shape_manual(values = c(
        "None" = "square filled", 
        "Geographical" = "circle filled",
        "Age/Qualification" = "circle filled", 
        "Age/Qual/AFLB" = "circle filled"
      )) + 
      labs(x = "Effect size", y = "") +
      scale_linetype_manual(name = "", values = c("95% c.i." = 1)) +
      my_theme()
